Equivalence Hypergraphs: E-Graphs for Monoidal Theories

### 2025-01-10 LICS/sections/conclusion.tex
some updates

In the future,  we intend to investigate a number of natural extensions to mathematical treatment of (acyclic) e-graphs developed here.
Some of the extensions that can be considered are: support for `functorial boxes'~\cite{mellies_functorial_2006} (in addition to e-boxes), which have a variety of applications, including the Cartesian-closure required for the implementation of functional programming languages~\cite{ghica-zanassi2023string}, as sketched in Fig. \ref{fig:app1}(a); the `spiders' used by the ZX-calculus to model quantum circuits~\cite{coecke_interacting_2011,ZX}, as sketched in Fig. \ref{fig:app1}(b); or trace~\cite{joyal_geometry_1991, Hasegawa-traced} which can be used to express feedback in categorical models of digital circuits~\cite{ghica_jung_2017,ghica_compositional_2023} and, indeed in conventional e-graphs to encode infinite equivalence classes, as sketched in Fig.~\ref{fig:app2}. All these application domains stand to benefit from the use of optimisation techniques, which in turn can take advantage of the appropriate e-graph technique.

\begin{figure}
\begin{subfigure}{0.45\linewidth}
\[
	\scalebox{0.75}{
	\tikzfig{../figures/conclusion/example-e-graphs_1}
	}
\]
\subcaption{\;} 
\end{subfigure}
\hfill
\begin{subfigure}{0.45\linewidth}
\[
	\scalebox{0.75}{
	\tikzfig{../figures/conclusion/example-e-graphs_2}
	}
\]
\subcaption{\;}
\end{subfigure}
\caption{E-(hyper)graphs for functorial boxes and the ZX-calculus}
\label{fig:app1}
\end{figure}

\begin{figure}
	\[
	\scalebox{0.65}{
	\tikzfig{../figures/conclusion/example-traced}
	}
\]
	\caption{E-graphs with cycles and e-hypergraphs with trace}
	\label{fig:app2}
\end{figure}

>>>>

In the future,  we intend to investigate a number of natural extensions to mathematical treatment of (acyclic) e-graphs developed here.
Some of the extensions that can be considered are: support for `functorial boxes'~\cite{mellies_functorial_2006} (in addition to e-boxes), which have a variety of applications, including the Cartesian-closure required for the implementation of functional programming languages~\cite{ghica-zanassi2023string}
% , as sketched in Fig. \ref{fig:app1}(a)
; the `spiders' used by the ZX-calculus to model quantum circuits~\cite{coecke_interacting_2011,ZX}
% , as sketched in Fig. \ref{fig:app1}(b)
; or trace~\cite{joyal_geometry_1991, Hasegawa-traced} which can be used to express feedback in categorical models of digital circuits~\cite{ghica_jung_2017,ghica_compositional_2023} and, indeed in conventional e-graphs to encode infinite equivalence classes
% , as sketched in Fig.~\ref{fig:app2}. 
All these application domains stand to benefit from the use of optimisation techniques, which in turn can take advantage of the appropriate e-graph technique.

% \begin{figure}
% \begin{subfigure}{0.45\linewidth}
% \[
% 	\scalebox{0.75}{
% 	\tikzfig{../figures/conclusion/example-e-graphs_1}
% 	}
% \]
% \subcaption{\;} 
% \end{subfigure}
% \hfill
% \begin{subfigure}{0.45\linewidth}
% \[
% 	\scalebox{0.75}{
% 	\tikzfig{../figures/conclusion/example-e-graphs_2}
% 	}
% \]
% \subcaption{\;}
% \end{subfigure}
% \caption{E-(hyper)graphs for functorial boxes and the ZX-calculus}
% \label{fig:app1}
% \end{figure}

% \begin{figure}
% 	\[
% 	\scalebox{0.65}{
% 	\tikzfig{../figures/conclusion/example-traced}
% 	}
% \]
% 	\caption{E-graphs with cycles and e-hypergraphs with trace}
% 	\label{fig:app2}
% \end{figure}
